Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis

### 2019-10-30 poster/conclusion.tex
Everything is aligned

Complementary filters can be used to \textbf{combine multiple sensors} in order
to obtain a \textbf{super sensor}.
Specification on the \textbf{super sensor noise} and on the \textbf{robustness
  of the sensor fusion} are linked to the \textbf{norm of the complementary filters}.
A synthesis method that permits the \textbf{shaping of the complementary filters
  norms} has been proposed and has been successfully applied for the design of
complex filters.

>>>>

Complementary filters can be used to \textbf{combine multiple sensors} in order
to obtain a \textbf{super sensor}.
Specification on the super sensor \textbf{noise} and on the \textbf{robustness
  of the sensor fusion} are linked to the \textbf{norm of the complementary filters}.
A synthesis method that permits the \textbf{shaping of the complementary filters
  norms} has been proposed and has been successfully applied for the design of
complex filters.
\vspace{0.5em}

### 2019-10-30 poster/ligo.tex
Everything is aligned

\begin{minipage}[t]{0.48\linewidth}
  The weights are designed such that their inverse magnitude is as
  close as possible to the specifications while being of reasonably \textbf{small order}
  (Fig.~\ref{fig:ligo_weights}).
  After synthesis, the obtained complementary filters are
  compared with the FIR filters \cite{hua05_low_ligo} and are found
  to be very close to each other (Fig.~\ref{fig:comp_fir_ligo_hinf}).
  \begin{tikzfigure}[Specifications and weights used for the $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[width=\linewidth]{figs/ligo_weights.pdf}
  \end{tikzfigure}
\end{minipage}\hfill
\begin{minipage}[t]{0.5\linewidth}
  \begin{tikzfigure}[Comparison of the FIR filters designed
    in \cite{hua05_low_ligo} (order 512) with the filters obtained with $\mathcal{H}_\infty$
    synthesis (order 28)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[width=\linewidth]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}

>>>>

\begin{minipage}[t]{0.48\linewidth}
  The weights are designed such that their inverse magnitude is as
  close as possible to the specifications while being of reasonably \textbf{small order}
  (Fig.~\ref{fig:ligo_weights}).

  \begin{tikzfigure}[Specifications and weights used for the
    $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[width=\linewidth]{figs/ligo_weights.pdf}
  \end{tikzfigure}
  \vspace{-0.8em}
  \begin{tabular}{ll}
    \(\tikz[baseline=-0.5ex]{\draw[color=mycolor1, line width=1.5pt](0,0)--(1,0)}\) & {\small Custom designed \(7^{\text{th}}\) Order Transfer Function}\\
    \(\tikz[baseline=-0.5ex]{\draw[color=mycolor2, line width=1.5pt](0,0)--(1,0)}\) & {\small Type I Chebyshev Filter (Order \(20\))}\\
  \end{tabular}
\end{minipage}\hfill
\begin{minipage}[t]{0.5\linewidth}
  \vspace{-1.0em}
  \begin{tikzfigure}[Comparison of the FIR filters designed
    in \cite{hua05_low_ligo} (order 512) with the filters obtained with $\mathcal{H}_\infty$
    synthesis (order 27)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[width=\linewidth]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}

After synthesis, the obtained complementary filters are
compared with the FIR filters \cite{hua05_low_ligo} and are found
to be very close to each other (Fig.~\ref{fig:comp_fir_ligo_hinf}).
